### 2017-02-17 Conclusion/Conclusion.tex
Adding some more of the crap at the beginning, plus editing

The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
125 GeV Higgs bosons was performed using 19.7 fb$^{-1}$ of data collected at a
centre of mass energy of 8 TeV during the 2012 \ac{LHC} data-taking period. Such a final
state can access areas of the MSSM phase space not easily accessible via other channels.
To separate more signal-like and more background-like events, a categorisation based on the number of 
b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-b
mass in a window around 125 GeV are used in combination with a kinematic fitting technique for
the reconstruction of the 4-body mass.
The resulting mass variable provides good separation between the signal and the dominant
\ttbar background, and is thus used as the variable for signal extraction. 
The results of this search are upper limits on production cross section times branching 
ratio, in a mass range $260<m_H<350$ GeV. A combination with a search for \AtoZhtolltautau
yields exclusion in the lowest \tanb~region of the low-tanb~MSSM scenario, as well
as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario.

Searches for a heavy neutral Higgs boson decaying into pairs of tau leptons were performed
using 2.3 fb$^{-1}$ of data recorded during the 2015
data-taking period of the \ac{LHC}, and using 12.9 fb$^{-1}$ of 
data recorded during the first half of the 2016 data-taking period. The 
branching ratio of heavy neutral Higgs bosons into di-\Pgt pairs is enhanced at high \tanb~in the \ac{MSSM},
making this one of the most sensitive search channels for such particles. The analysis uses a categorisation 
based on the presence of b-tagged jets to separate
the gluon fusion and b-associated production modes of Higgs bosons in the \ac{MSSM}. 
The hadronic tau isolation working point, as well as the topological selection on 
the \mT~variable, are chosen to optimise the search sensitivity for signal
masses of around 1 TeV.
The sensitivity is maximised by using the \mTtot~variable for signal extraction.
This variable separates the dominant backgrounds
and the high-mass signal well.
No significant excess is observed in these searches, and so 
these analyses set limits on the production cross section times branching ratio of both the
gluon fusion and b-associated production processes. The results are also
interpreted in MSSM benchmark scenarios, where the analyses exclude large areas
of the \mA-\tanb~plane, with significant improvement with respect to the most sensitive
results obtained in Run 1. A combination of the 2015 and 2016 analyses is also
performed. This combination improves on the results of the 2016 analysis alone, thus
setting the most stringent limits on this process to date.

As more data are collected during the remainder of Run 2, and in the 
future, searches for MSSM Higgs bosons in the di-$\Pgt$ final
state will continue. If no such Higgs bosons are found, these searches
will be able to exclude even more of the \mA-\tanb~plane in specific
MSSM benchmark scenarios, although not all of the \mA-\tanb~plane
will become accessible. A projection of the results of the 2015 \ac{MSSM}
analysis to an integrated luminosity of 300 fb$^{-1}$ and 3000 fb$^{-1}$ is
shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
3000 fb$^{-1}$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
as the branching ratio of $\PHiggsps/\PHiggs$ into di-$\Pgt$ pairs 
is very low in the high \mA-low \tanb~corner. This region can be accessed 
via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
has an enhanced branching ratio in this region. To fully cover the still
available phase space it will therefore start to become more and more
important to combine searches for heavy Higgs bosons in different final states.
Doing this will give the best sensitivity to possible
heavy Higgs bosons - or in the absence of these particles exclusion
of the scenarios that predict them.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/scenario_comp2.pdf}
\end{center}
\caption{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
 at 95\% CL of the 2015 MSSM analysis (pink)
projected to an integrated luminosity of 300 fb$^{-1}$ (blue) and 3000 fb$^{-1}$ (red)
under several assumptions of how the systematic uncertainties scale. Even with an integrated 
luminosity of 3000 fb$^{-1}$ it is not possible to exclude the entire \mA-\tanb~plane
in this \ac{MSSM} benchmark scenario \cite{HTT-projection}.}
\label{fig:mssm_projection_fig}
\end{figure}

>>>>

The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
$125\,\GeV$ Higgs bosons was performed using $19.7\,\invfb$ of data collected at a
centre of mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
state can access areas of the MSSM phase space not easily accessible via other channels.
To separate more signal-like and more background-like events, a categorisation based on the number of 
b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-b
mass in a window around $125\,\GeV$ are used in combination with a kinematic fitting technique for
the reconstruction of the 4-body mass.
The resulting mass variable provides good separation between the signal and the dominant
\ttbar background, and is thus used as the variable for signal extraction. 
The results of this search are upper limits on production cross section times branching 
ratio, in a mass range $260<m_H<350\,\GeV$. A combination with a search for \AtoZhtolltautau
yields exclusion in the lowest \tanb~region of the low-\tanb~MSSM scenario, as well
as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario \cite{CMS-HIG-14-034}.

Searches for a heavy neutral Higgs boson decaying into pairs of tau leptons were performed
using $2.3\,\invfb$ of data recorded during the 2015
data-taking period of the \ac{LHC}, and using $12.9\,\invfb$ of 
data recorded during the first half of the 2016 data-taking period. The 
branching ratio of heavy neutral Higgs bosons into di-tau pairs is enhanced at high \tanb~in the \ac{MSSM},
making this one of the most sensitive search channels for such particles. Both analyses use a categorisation 
based on the presence of b-tagged jets to separate
the gluon fusion and b-associated production modes of Higgs bosons in the \ac{MSSM}. 
The hadronic tau isolation working point, as well as the topological selection on 
the \mT~variable, are chosen to optimise the search sensitivity for signal
masses of around $1\,\TeV$.
The sensitivity is maximised by using the \mTtot~variable for signal extraction.
This variable separates the dominant backgrounds
and the high-mass signal well.
No significant excess is observed in these searches, and so 
these analyses set limits on the production cross section times branching ratio of both the
gluon fusion and b-associated production processes. The results are also
interpreted in MSSM benchmark scenarios, where the analyses exclude large areas
of the \mA-\tanb~plane, with significant improvement with respect to the most sensitive
results obtained in Run 1 \cite{CMS-PAS-HIG-16-006,CMS-PAS-HIG-16-037}. A combination of the 2015 and 2016 analyses is also
performed. This combination improves on the results of the 2016 analysis alone, thus
setting the most stringent limits on this process to date.

As more data are collected during the remainder of Run 2, and in the 
future, searches for MSSM Higgs bosons in the di-tau final
state will continue. If no such Higgs bosons are found, these searches
will be able to exclude even more of the \mA-\tanb~plane in specific
MSSM benchmark scenarios, although not all of the \mA-\tanb~plane
will become accessible. A projection of the results of the 2015 \ac{MSSM}
analysis to an integrated luminosity of $300\,\invfb$ and $3000\,\invfb$, presented at ECFA \cite{HTT-projection}, is
shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
$3000\,\invfb$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
as the branching ratio of $\PHiggsps/\PHiggs$ into di-tau pairs 
is very low in the high \mA-low \tanb~corner. This region can be accessed 
via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
has an enhanced branching ratio in this region. To fully cover the still
available phase space it will therefore start to become more and more
important to combine searches for heavy Higgs bosons in different final states.
Doing this will give the best sensitivity to possible
heavy Higgs bosons - or in the absence of these particles exclusion
of the scenarios that predict them.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/scenario_comp2.pdf}
\end{center}
\caption[The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
at 95\% CL of the 2015 MSSM analysis, projected to an integrated luminosity of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
 at 95\% CL of the 2015 MSSM analysis (pink)
projected to an integrated luminosity of $300\,\invfb$ (blue) and $3000\,\invfb$ (red)
under several assumptions of how the systematic uncertainties scale. Even with an integrated 
luminosity of $3000\,\invfb$ it is not possible to exclude the entire \mA-\tanb~plane
in this \ac{MSSM} benchmark scenario \cite{HTT-projection}.}
\label{fig:mssm_projection_fig}
\end{figure}

### 2017-02-17 Detector/Detector.tex
Adding some more of the crap at the beginning, plus editing

\subsection{\acl{ECAL}}
\label{sec:CMSLHC_CMS_ecal}
The \ac{ECAL} \cite{cms-jinst} is a hermetic homogeneous calorimeter
made of nearly $76\,000$ lead tungstate (PbWO$_4$) crystals. It has very
good energy resolution, is highly granular and has a fast response, all qualities 
which are needed to be able to detect $\PHiggslight\rightarrow \Pphoton\Pphoton$ decays.

@@

Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
the sub-systems it is made up of. The \ac{EB} 
covers the pseudorapidity range up to $|\eta|<1.479$, with
crystals of $0.0174 \times 0.0174$ in $\eta$-$\phi$. The \ac{EE}
provide coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$.
Each endcap is divided into two halves. The preshower detectors, 
which are sampling calorimeters placed in front of the endcaps, cover a range of $1.653<|\eta|<2.6$.
The main use of the preshower detectors is to identifiy neutral pions decaying to two photons in the 
endcaps. Additionally,
they aid in the identification of electrons and improve the resolution
of the position determination. Each of the two preshower detectors consists
of two layers of lead radiators to initiate the shower, with silicon sensors
placed after each layer of radiators to measure the deposited energy. The 
total thickness of the preshower is three radiation lengths.

@@

\subsection{\acl{HCAL}}
\label{sec:CMSLHC_CMS_hcal}
The \ac{ECAL} is surrounded by the \ac{HCAL} \cite{cms-jinst}, which is needed for the
measurement of the energies of strongly interacting particles. As
the \ac{ECAL} extends out to a radius of $1.77\,\metre$ and the magnet coil
starts at a radius of $2.95\,\metre$, space for the \ac{HCAL} inside the magnet
coil is limited. The \ac{HCAL} design takes
this into account by placing part of the calorimeter outside the magnet coil. An
illustration of a quadrant of the
\ac{HCAL}, indicating the positions of the sub-systems, is shown
in figure \ref{fig:CMS_HCAL}.

@@

The \ac{CMS} muon system \cite{cms-jinst} is composed of three sub-systems which
are all necessary to ensure the identification requirements can be met. The muon system is located
outside of the magnet coil, interspersed in the iron return yoke of the solenoid.
In the barrel of the detector the \ac{DTs} provide coverage for $|\eta|<1.2$, with
the \ac{CSCs} covering the $0.9<|\eta|<2.4$ region. The \ac{RPCs}, covering the same
regions as both the \ac{DTs} and \ac{CSCs}, are used as a dedicated triggering system.

A cross section of one quadrant of the detector, indicating
the positions of the \ac{DTs}, \ac{CSCs} and \ac{RPCs}, is shown in figure \ref{fig:CMS_MuonSystem}.
The top of the fourth muon endcap station as shown in this figure was added during \ac{LS1} \cite{cms-muon-upgrade}, providing
additional layers of \ac{CSCs} and \ac{RPCs}.
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./Detector/Plots/MuonSystemUpgrade.png}
\caption[Cross section of one quadrant of the CMS detector,
indicating the positions of the different muon system components.]{Cross section of one quadrant of the CMS detector, indicating
the positions of the different muon system components \cite{cms-muon-upgrade}. The 
fourth muon endcap stations were extended during \ac{LS1}; in Run 1 only the lower
part existed.}
\label{fig:CMS_MuonSystem}
\end{center}
\end{figure}

The \ac{DTs} consists of layers of drift cells which have a cross section of $4.2\,\cm \times 1.3\,\cm$ and
are $2.4\,\metre$ long. The cells are filled with a mixture of %85\% 
argon gas and carbon dioxide gas.
Muons passing through the chamber ionise the gas, freeing electrons
which drift towards the anode wire running along the centre of the tube-shaped cell. 
This gives rise to an electric signal. There are four drift tube stations in each wedge of 
the detector, each in turn consisting of 8 to 12 layers of drift tubes. Some of
these layers are oriented parallel to the beam line, providing a measurement of $\phi$.
There are also layers oriented orthogonal to the beam line, which give a measurement
of the $z$ coordinate. Measurements of the spatial resolution were made
during p-p running in 2010.
The spatial resolution of the \ac{DTs} is $80$--$120\,\micron$ per chamber for
measurements in the $\phi$ direction, while the resolution of the $z$ measurement
is $130$--$400\,\micron$ \cite{cms-muon-7tev}. %Drift lines distorted by magnetic field parallel to the wires

In the endcaps, where both the muon rate and the radiation levels are higher, the \ac{CSCs} provide
measurements of the muon track. These detectors are radiation hard,
and have a fast response and fine segmentation.
Each of the CSC modules is a wedge-shaped
multi-wire proportional chamber %WTF
with six gaseous chambers bounded by cathode plates. Sensitive
strips are placed on these plates in the 
radial direction, to measure the muon coordinate in the  $r$--$\phi$ plane.
Anode wires between the cathode planes
run along the $\phi$ direction and provide a measurement of
$\eta$. The resolution of the $r$--$\phi$ measurement is $40$--$120\,\micron$ \cite{cms-muon-7tev}.

In addition to the \ac{DTs} and \ac{CSCs}, the \ac{RPCs} provide coverage
for $|\eta|<1.6$. These are made up of parallel plates, forming the anode and cathode,
with a gas gap in between. Ionisation of the gas due to the passing
muons is read out using aluminium strips running parallel to the 
beam axis. The position resolution of the \ac{RPCs} is poorer than
that of the \ac{DTs} and \ac{CSCs}, but their time response is very fast. As
a result of this the \ac{RPCs} are used as an independent muon trigger
which can correctly identify the beam crossing from which the muon
originated.

@@

Hits in the muon chambers are read out and passed to the track finder layer 
of the muon trigger, which combines information from the CSC, DT
and RPC systems in regions of $\eta$-$\phi$.
In further layers of the muon trigger the information from different
regions is combined, until finally the global muon trigger
can return a sorted list of the best muon candidates to the global trigger.
The global trigger combines the information from the calorimeter and muon triggers
to make a decision on whether the event should be sent to the \ac{HLT} or whether
it should be discarded. A decision has to be made within $3.2\,\micro\second$, the maximum time during
which data can be stored in the \ac{L1} trigger before being lost.

>>>>

\subsection{Electromagnetic calorimeter}
\label{sec:CMSLHC_CMS_ecal}
The \ac{ECAL} \cite{cms-jinst} is a hermetic homogeneous calorimeter
made of nearly $76\,000$ lead tungstate (PbWO$_4$) crystals. It has very
good energy resolution, is highly granular and has a fast response, all qualities 
which are needed to be able to detect $\PHiggslight\rightarrow \Pphoton\Pphoton$ decays.

@@

Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
the sub-systems it is made up of. The \ac{EB} 
covers the pseudorapidity range up to $|\eta|<1.479$, with
crystals of $0.0174 \times 0.0174$ in $\eta$-$\phi$. The \acp{EE}
provide coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$.
Each endcap is divided into two halves. The preshower detectors, 
which are sampling calorimeters placed in front of the endcaps, cover a range of $1.653<|\eta|<2.6$.
The main use of the preshower detectors is to identifiy neutral pions decaying to two photons in the 
endcaps. Additionally,
they aid in the identification of electrons and improve the resolution
of the position determination. Each of the two preshower detectors consists
of two layers of lead radiators to initiate the shower, with silicon sensors
placed after each layer of radiators to measure the deposited energy. The 
total thickness of the preshower is three radiation lengths.

@@

\subsection{Hadron calorimeter}
\label{sec:CMSLHC_CMS_hcal}
The \ac{ECAL} is surrounded by the \ac{HCAL} \cite{cms-jinst}, which is needed for the
measurement of the energies of strongly interacting particles. As
the \ac{ECAL} extends out to a radius of $1.77\,\metre$ and the magnet coil
starts at a radius of $2.95\,\metre$, space for the \ac{HCAL} inside the magnet
coil is limited. The \ac{HCAL} design takes
this into account by placing part of the calorimeter outside the magnet coil. An
illustration of a quadrant of the
\ac{HCAL}, indicating the positions of the sub-systems, is shown
in figure \ref{fig:CMS_HCAL}.

@@

The \ac{CMS} muon system \cite{cms-jinst} is composed of three sub-systems which
are all necessary to ensure the identification requirements can be met. The muon system is located
outside of the magnet coil, interspersed in the iron return yoke of the solenoid.
In the barrel of the detector the \acp{DT} provide coverage for $|\eta|<1.2$, with
the \acp{CSC} covering the $0.9<|\eta|<2.4$ region. The \acp{RPC}, covering the same
regions as both the \acp{DT} and \acp{CSC}, are used as a dedicated triggering system.

A cross section of one quadrant of the detector, indicating
the positions of the \acp{DT}, \acp{CSC} and \acp{RPC}, is shown in figure \ref{fig:CMS_MuonSystem}.
The top of the fourth muon endcap station as shown in this figure was added during \ac{LS1} \cite{cms-muon-upgrade}, providing
additional layers of \acp{CSC} and \acp{RPC}.
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./Detector/Plots/MuonSystemUpgrade.png}
\caption[Cross section of one quadrant of the CMS detector,
indicating the positions of the different muon system components.]{Cross section of one quadrant of the CMS detector, indicating
the positions of the different muon system components \cite{cms-muon-upgrade}. The 
fourth muon endcap stations were extended during \ac{LS1}; in Run 1 only the lower
part existed.}
\label{fig:CMS_MuonSystem}
\end{center}
\end{figure}

The \acp{DT} consist of layers of drift cells which have a cross section of $4.2\,\cm \times 1.3\,\cm$ and
are $2.4\,\metre$ long. The cells are filled with a mixture of %85\% 
argon gas and carbon dioxide gas.
Muons passing through the chamber ionise the gas, freeing electrons
which drift towards the anode wire running along the centre of the tube-shaped cell. 
This gives rise to an electric signal. There are four drift tube stations in each wedge of 
the detector, each in turn consisting of 8 to 12 layers of drift tubes. Some of
these layers are oriented parallel to the beam line, providing a measurement of $\phi$.
There are also layers oriented orthogonal to the beam line, which give a measurement
of the $z$ coordinate. Measurements of the spatial resolution were made
during p-p running in 2010.
The spatial resolution of the \acp{DT} is $80$--$120\,\micron$ per chamber for
measurements in the $\phi$ direction, while the resolution of the $z$ measurement
is $130$--$400\,\micron$ \cite{cms-muon-7tev}. %Drift lines distorted by magnetic field parallel to the wires

In the endcaps, where both the muon rate and the radiation levels are higher, the \acp{CSC} provide
measurements of the muon track. These detectors are radiation hard,
and have a fast response and fine segmentation.
Each of the \ac{CSC} modules is a wedge-shaped
multi-wire proportional chamber %WTF
with six gaseous chambers bounded by cathode plates. Sensitive
strips are placed on these plates in the 
radial direction, to measure the muon coordinate in the  $r$--$\phi$ plane.
Anode wires between the cathode planes
run along the $\phi$ direction and provide a measurement of
$\eta$. The resolution of the $r$--$\phi$ measurement is $40$--$120\,\micron$ \cite{cms-muon-7tev}.

In addition to the \acp{DT} and \acp{CSC}, the \acp{RPC} provide coverage
for $|\eta|<1.6$. These are made up of parallel plates, forming the anode and cathode,
with a gas gap in between. Ionisation of the gas due to the passing
muons is read out using aluminium strips running parallel to the 
beam axis. The position resolution of the \acp{RPC} is poorer than
that of the \acp{DT} and \acp{CSC}, but their time response is very fast. As
a result of this the \acp{RPC} are used as an independent muon trigger
which can correctly identify the beam crossing from which the muon
originated.

@@

Hits in the muon chambers are read out and passed to the track finder layer 
of the muon trigger, which combines information from the \ac{CSC}, \ac{DT}
and \ac{RPC} systems in regions of $\eta$-$\phi$.
In further layers of the muon trigger the information from different
regions is combined, until finally the global muon trigger
can return a sorted list of the best muon candidates to the global trigger.
The global trigger combines the information from the calorimeter and muon triggers
to make a decision on whether the event should be sent to the \ac{HLT} or whether
it should be discarded. A decision has to be made within $3.2\,\micro\second$, the maximum time during
which data can be stored in the \ac{L1} trigger before being lost.

### 2017-02-17 MSSM/MSSM.tex
Edit of objects section
Adding some more of the crap at the beginning, plus editing

\section{Datasets and MC samples}
\label{sec:mssm_datasets}
The dataset used for this analysis corresponds to an integrated 
luminosity of 12.9 fb$^{-1}$ collected at a centre--of--mass
energy of 13 TeV during the first half of
the 2016 p--p running period of the \ac{LHC}. %Section
%\ref{sec:mssm_combination} includes the combination of this
%dataset with a dataset collected during the 2015 p--p running
%period of the \ac{LHC}. This dataset corresponds to an integrated
%luminosity of 2.3 fb$^{-1}$ collected at $\sqrt{s} = 13$ TeV.

@@

Because the triggers involving electrons or muons reach 
their maximum efficiency as a function of \pT~quickly, the offline \pT~cut
on the electrons and muons is 1 GeV above the \pT~threshold of the trigger. The
hadronic tau efficiency turns on much more slowly, and therefore the offline \pT~cut
on the hadronic taus in the \tautau channel is 5 GeV above the trigger \pT~threshold.
In addition, a requirement is made on the $\eta$ of the electrons, muons and
hadronic taus. This election is driven by the $\eta$ range covered by the tracker and
that is thus used for the reconstruction of the particles. For some of the
channels the used trigger is restricted in $\eta$. If that is the case
then the cut is chosen to align with the trigger restrictions.
As an illustration figure \ref{fig:mt_muonpt}b shows
the $\eta$ distribution for electrons in the \etau channel, again with the signal overlaid.
The signal peaks in the central $\eta$ region.

Other selections include cuts on the impact parameters $d_{xy}$ and $d_{z}$, which
ensure that the particle is likely to have
originated from the primary vertex. This reduces the number of selected particles
which come from pile--up interactions.
Additional identification and isolation criteria
are also applied; these will be discussed in sections \ref{sec:mssm_eventsel_pairs}--\ref{sec:mssm_eventsel_em}.
The optimisation of some of the selections will also be discussed there. Note that 
the optimisations were all based on the dataset collected during the 2015 p-p running period of the \ac{LHC}, which
corresponds to an integrated luminosity of 2.3 fb$^{-1}$.

@@

\section{\ac{MC} to data correction factors}

@@

\section{Background estimation}
\label{sec:mssm_bkgs}
There are several backgrounds in this analysis, and the different final
states can have different background compositions. Consider figure \ref{fig:mssm_bkgs_overview}a,
which shows the low $m_{\text{T}}^{\text{tot}}$ region in the no b-tag category
of the \mutau channel and figure \ref{fig:mssm_bkgs_overview}b, which shows the low $m_{\text{T}}^{\text{tot}}$
region in the b-tag category of the \emu channel. These regions are where the backgrounds are concentrated and it
is therefore easier to see the different contributions. \Ztautau is a background in all four channels as 
it has two real taus in the final state, like the signal that we are searching for. 
Smaller backgrounds 
from \Zellell decays also play a role, especially in the \mutau and \etau channels where such events
might pass the selection if for example a jet is misreconstructed as a hadronic tau and only one of the leptons is reconstructed. 
Production of QCD multijet events, labelled `QCD' on the plots in figure \ref{fig:mssm_bkgs_overview}, is a background when 
two jets are misreconstructed as the two particles of the candidate pair. %Relatively likely to happen in tautau channel
As visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$, and so such events nearly 
always contain real b-jets. The decay products  of one or both of the \PW bosons, and additional jets in the event, can 
then form \etau, \mutau, \tautau and \emu pairs.\\
The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW decay and a jet misreconstructed
as a hadronic tau form a pair. In the \tautau channel it is a background when the \PW decays into $\Pgt\Pgn$ with the tau 
decaying hadronically and an additional jet in the event is misreconstructed as a hadronic tau, or when two jets are
reconstructed as hadronic taus.
In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
channel this background is smaller. Backgrounds that are small in all channels are the di-boson and single-top backgrounds. In 
figures showing the backgrounds the di-boson and single-top backgrounds are drawn together with the \Wjets 
background as the `Electroweak' component.

>>>>

\section{Datasets and \acs{MC} samples}
\label{sec:mssm_datasets}
The dataset used for this analysis corresponds to an integrated 
luminosity of 12.9 fb$^{-1}$ collected at a centre--of--mass
energy of 13 TeV during the first half of
the 2016 p--p running period of the \ac{LHC}. %Section
%\ref{sec:mssm_combination} includes the combination of this
%dataset with a dataset collected during the 2015 p--p running
%period of the \ac{LHC}. This dataset corresponds to an integrated
%luminosity of 2.3 fb$^{-1}$ collected at $\sqrt{s} = 13$ TeV.

@@

Because the triggers involving electrons or muons reach 
their maximum efficiency as a function of \pT~quickly, the offline \pT~cut
on the electrons and muons is 1 GeV above the \pT~threshold of the trigger. The
hadronic tau efficiency turns on much more slowly, and therefore the offline \pT~cut
on the hadronic taus in the \tautau channel is 5 GeV above the trigger \pT~threshold.
In addition, a requirement is made on the $\eta$ of the electrons, muons and
hadronic taus. This selection is driven by the $\eta$ range covered by the tracker and
that is thus used for the reconstruction of the particles. For some of the
channels the used trigger is restricted in $\eta$. If that is the case
then the cut is chosen to align with the trigger restrictions.
As an illustration figure \ref{fig:mt_muonpt}b shows
the $\eta$ distribution for electrons in the \etau channel, again with the signal overlaid.
The signal peaks in the central $\eta$ region.

Other selections include cuts on the transverse and longitudinal impact parameters $d_{xy}$ and $d_{z}$, which
ensure that the particle is likely to have
originated from the primary vertex. This reduces the number of selected particles
which come from pile--up interactions.
Additional identification and isolation criteria
are also applied; these will be discussed in sections \ref{sec:mssm_eventsel_pairs}--\ref{sec:mssm_eventsel_em}.
The optimisation of some of the selections will also be discussed there. Note that 
the optimisations were all based on the dataset collected during the 2015 p-p running period of the \ac{LHC}, which
corresponds to an integrated luminosity of 2.3 fb$^{-1}$.

@@

\section{\acs{MC} to data correction factors}

@@

\section{Background estimation}
\label{sec:mssm_bkgs}
There are several backgrounds in this analysis, and the different final
states can have different background compositions. Consider figure \ref{fig:mssm_bkgs_overview}a,
which shows the low $m_{\text{T}}^{\text{tot}}$ region in the no b-tag category
of the \mutau channel and figure \ref{fig:mssm_bkgs_overview}b, which shows the low $m_{\text{T}}^{\text{tot}}$
region in the b-tag category of the \emu channel. These regions are where the backgrounds are concentrated and it
is therefore easier to see the different contributions. \Ztautau is a background in all four channels as 
it has two real taus in the final state, like the signal that we are searching for. 
Smaller backgrounds 
from \Zellell decays also play a role, especially in the \mutau and \etau channels where such events
might pass the selection if for example a jet is misreconstructed as a hadronic tau and only one of the leptons is reconstructed. 
Production of QCD multijet events, labelled `QCD' on the plots in figure \ref{fig:mssm_bkgs_overview}, is a background when 
two jets are misreconstructed as the two tau candidates. %Relatively likely to happen in tautau channel
As is visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$, and so such events nearly 
always contain real b-jets. The decay products  of one or both of the \PW bosons, and additional jets in the event, can 
then form \etau, \mutau, \tautau and \emu pairs.\\
The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW decay and a jet misreconstructed
as a hadronic tau form a pair. In the \tautau channel it is a background when the \PW decays into $\Pgt\Pgn$ with the tau 
decaying hadronically and an additional jet in the event is misreconstructed as a hadronic tau, or when two jets are
reconstructed as hadronic taus.
In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
channel this background is smaller. Backgrounds that are small in all channels are the di-boson and single-top backgrounds. In 
figures showing the backgrounds the di-boson and single-top backgrounds are drawn together with the \Wjets 
background and is referred to as the `Electroweak' component.
